Towards Verifying the Bitcoin-S Library

### 2019-07-02 paper/paper.tex
more work on transformations

\begin{figure}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/reduced-nocomments/number/NumberType.scala}
  \caption{Extracted Code from NumberType.scala}
  \label{fig:numbertype}
\end{figure}

\begin{figure}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/reduced-nocomments/currency/CurrencyUnits.scala}
  \caption{Extracted Code from CurrencyUnits.scala}
  \label{fig:currencyunits}
\end{figure}

@@

by:
\begin{lstlisting}[style=scala]
  lazy val min = Int64(BigInt(-9223372036854775808L))
  lazy val max = Int64(BigInt(9223372036854775807L))
}
\end{lstlisting}

>>>>

\begin{figure}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/reduced/number/NumberType.scala}
  \caption{Extracted Code from NumberType.scala}
  \label{fig:numbertype}
\end{figure}

\begin{figure}
\lstinputlisting[style=scala]{../code/addition/src/main/scala/reduced/currency/CurrencyUnits.scala}
  \caption{Extracted Code from CurrencyUnits.scala}
  \label{fig:currencyunits}
\end{figure}

@@

by:
\begin{lstlisting}[style=scala]
  lazy val min = Int64(BigInt(-9223372036854775808L))
  lazy val max = Int64(BigInt(9223372036854775807L))
\end{lstlisting}
